# Loading packages
```{r}
library(tidyverse)
library(dplyr)
library(tidyr)
```

# Loading dataset
```{r}
team_statistics <- read.csv("cbb.csv")
```

# Previewing dataset
```{r}
head(team_statistics)
```

# Getting rid of BARTHAG variable 
```{r}
team_statistics$BARTHAG <- NULL 
```

# Defining the variable SEED as an integer
```{r}
team_statistics$SEED <- as.integer(team_statistics$SEED)
```

# Renaming the placements of the POSTSEASON variable 
```{r}
team_statistics$POSTSEASON <- replace(team_statistics$POSTSEASON, team_statistics$POSTSEASON  == "Champions", "Champion")
team_statistics$POSTSEASON <- replace(team_statistics$POSTSEASON, team_statistics$POSTSEASON  == "2ND", "Runner-up")
team_statistics$POSTSEASON <- replace(team_statistics$POSTSEASON, team_statistics$POSTSEASON  == "F4", "Final Four")
team_statistics$POSTSEASON <- replace(team_statistics$POSTSEASON, team_statistics$POSTSEASON  == "E8", "Elite Eight")
team_statistics$POSTSEASON <- replace(team_statistics$POSTSEASON, team_statistics$POSTSEASON  == "S16", "Sweet Sixteen")
team_statistics$POSTSEASON <- replace(team_statistics$POSTSEASON, team_statistics$POSTSEASON  == "R32", "Second Round")
team_statistics$POSTSEASON <- replace(team_statistics$POSTSEASON, team_statistics$POSTSEASON  == "R64", "First Round")
team_statistics$POSTSEASON <- replace(team_statistics$POSTSEASON, team_statistics$POSTSEASON  == "R68", "First Four")
team_statistics$POSTSEASON <- replace(team_statistics$POSTSEASON, team_statistics$POSTSEASON  == "N/A", NA)
```

# Filtering dataset down to only teams that made the tournament 
```{r}
team_statistics <- filter(team_statistics, !is.na(POSTSEASON))
```

# Creating L variable
```{r}
team_statistics <- mutate(team_statistics, L = G - W)
```

# Creating RECORD variable
```{r}
team_statistics <- mutate(team_statistics, RECORD = paste(W, "-", L))

```

# Creating WINPCT variable 
```{r}
team_statistics <- mutate(team_statistics, WINPCT = W / G)
team_statistics <- mutate(team_statistics, WINPCT = round(WINPCT, 3))
```

# Reordering columns 
```{r}
team_statistics <- relocate(team_statistics, L, .after = W)
team_statistics <- relocate(team_statistics, RECORD, .after = G)
team_statistics <- relocate(team_statistics, WINPCT, .after = L)
```

# Arranging columns by TEAM and YEAR
```{r}
team_statistics <- arrange(team_statistics, YEAR, TEAM)
```

# Viewing final table 
```{r}
view(team_statistics)
```